Implementing simplified INLA into `aghq`

### 2022-11-01 src/dev_sinla/sinla.Rmd
Rename model1index to model1_index

```{r}
compile("model1index.cpp")
dyn.load(dynlib("model1index"))
```

The `prepare_dat` function takes `dat` and makes it compatible with `model1index` for particular choice of marginal `i`.

@@

#' random are integrated out with a Laplace approximation
obj <- MakeADFun(
  data = dat_i,
  parameters = param_i,
  random = "phi_prev_minus_i",
  DLL = "model1index",
  silent = TRUE
)

@@

obj_fixed_theta <- MakeADFun(
  data = dat_i,
  parameters = param_i_fixed_theta,
  random = "phi_prev_minus_i",
  DLL = "model1index",
  silent = TRUE,
  map = map_fixed_theta
)
```

@@

  obj_fixed_theta <- MakeADFun(
    data = dat_i,
    parameters = param_i_fixed_theta,
    random = "phi_prev_minus_i",
    DLL = "model1index",
    silent = TRUE,
    map = map_fixed_theta
  )

@@

## `model1index.cpp`

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines('model1index.cpp')}
```

>>>>

```{r}
compile("model1_index.cpp")
dyn.load(dynlib("model1_index"))
```

The `prepare_dat` function takes `dat` and makes it compatible with `model1_index` for particular choice of marginal `i`.

@@

#' random are integrated out with a Laplace approximation
obj <- MakeADFun(
  data = dat_i,
  parameters = param_i,
  random = "phi_prev_minus_i",
  DLL = "model1_index",
  silent = TRUE
)

@@

obj_fixed_theta <- MakeADFun(
  data = dat_i,
  parameters = param_i_fixed_theta,
  random = "phi_prev_minus_i",
  DLL = "model1_index",
  silent = TRUE,
  map = map_fixed_theta
)
```

@@

  obj_fixed_theta <- MakeADFun(
    data = dat_i,
    parameters = param_i_fixed_theta,
    random = "phi_prev_minus_i",
    DLL = "model1_index",
    silent = TRUE,
    map = map_fixed_theta
  )

@@

## `model1_index.cpp`

```{cpp, echo=TRUE, eval=FALSE, output.var="ex", code=readLines('model1_index.cpp')}
```
